Environmental stress drives intermediate plant and pollinator specialisation

### 2020-04-18 paper/manuscript.Rmd
Add gbif citations

---
title: "Environmental stress drives intermediate plant and pollinator specialisation"
author: 
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
# geometry: 
  # - textwidth=33em
  # - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage{caption}
editor_options: 
  chunk_output_type: console
---

@@

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
loadd(interaction_citations, config) 
loadd(bibliography)
```

@@

The niche factor analysis requires two critical pieces of information. 
First, it requires information about the occurrences of the species of interest.
Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility (GBIF; https://www.gbif.org). 
Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
We, therefore, followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
We integrated the occurrence records from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.

>>>>

---
title: "Environmental stress drives intermediate plant and pollinator specialisation"
author: 
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
  - occurrence_bibliography.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
# geometry: 
  # - textwidth=33em
  # - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage{caption}
editor_options: 
  chunk_output_type: console
---

@@

loadd(abs_wordcount, msc_wordcount, n_displays, n_references, keywords, bibliography)
loadd(interaction_citations, config) 
loadd(bibliography, occurrence_refs)
```

@@

```{r occurrence-citations}
occ_cit <- occurrence_refs %>%
  purrr::map_chr(names) %>%
  paste0("@", .) %>%
  paste(collapse = "; ") %>%
  paste0("[", ., "]")
```

The niche factor analysis requires two critical pieces of information. 
First, it requires information about the occurrences of the species of interest.
Second, the method requires information about the environmental conditions for all the locations in which the species occurs.
We retrieved `r round(sum(n_occurrences$N)/1000000, digits = 1)` million occurrences of our focal species from the Global Biodiversity Information Facility `r occ_cit`. 
Issues with data quality are a central issue hampering the use of publicly available species occurrence GBIF data in ecology and biogeography [@jetz_essential_2019]. 
We, therefore, followed a series of filters and geographic heuristics to correct or remove erroneous and imprecise referencing records [see supplementary methods; @zizka_coordinatecleaner_2019] which allowed us to identify and remove `r round(sum(n_dirty_occurrences$N)/1000000, digits = 1)` million potentially problematic occurrences from further analysis.
We integrated the occurrence records from our plant-pollinator communities to the cleaned occurrences retrieved from GBIF.
